Renal IV

### 2017-06-07 renal1.rmd
updated a couple of lines

-  minimal change (children; bowmans space epithelial cells loses its negative charge, so not much morphological change)
-  Membranous glomerulonephritis:
-  Focal segmental glomerulosclerosis (FSGS): adults

>>>>

-  minimal change (children; bowmans space epithelial cells loses its negative charge, so not much morphological change)
-  Membranous glomerulonephritis: *sub-epithelial deposits* of immune complexes (type III hypersensitivity)
-  Focal segmental glomerulosclerosis (FSGS): adults

### 2017-06-07 renal4.rmd
updated a couple of lines

-  Clavulanic acid contains beta-lactam, gets preferentially broken down by resistant bacteria. Therefore penicillin and cephalosporins can have an effect.
-  Receptors
    -  M~3~: ACh from parasympathetic pelvic nerve to contract detrusor
    -  B~3~: hypogastric N (sym): noradrenaline relaxation of detrusor
    -  $\alpha_{1}$ in the int sphincter: hypogastric N: contraction of ext sphincter
    -  Nicotinic in the ext sphincter: somatic from pudendal nerve to contract it
    -  Also sensory N AFFERENT in detrusor that is stimulated when bladder is stretched

>>>>

-  Learn bladder Ca
    -  Smoking is major risk factor. Can present as painless haematuria
-  Major mech of stress incontinence: *urethral hypermobility*
-  *Proteus mirabilis* is a gram(-) rod that leads to highly alkaline urine
-  Medication associated with acute urinary retention: decongenstant
-  Enuresis: bedwetting during sleep in child >6
-  Pharm Mx of BPH: $\alpha$-adrenergic receptor antagonists
-  Clavulanic acid contains beta-lactam, gets preferentially broken down by resistant bacteria. Therefore penicillin and cephalosporins can have an effect.
-  Receptors
    -  M~3~: ACh from parasympathetic pelvic nerve to contract detrusor
    -  B~3~: hypogastric N (sym): noradrenaline relaxation of detrusor
    -  $\alpha_{1}$ in the int sphincter: hypogastric N: contraction of ext sphincter
    -  Nicotinic in the ext sphincter: somatic from pudendal nerve to contract it
    -  Also sensory N AFFERENT in detrusor that is stimulated when bladder is stretched
-  Calculi:
    -  Struvite likely to be from infn
